\documentclass[stu,12pt]{apa7}
  \usepackage{times}               % Times New Roman Font Face
  \usepackage[american]{babel}      % Localization
  \usepackage[utf8]{inputenc}      % Input Encoding
  \usepackage{hyperref}            % Hyperlinks
  \usepackage{enumitem}            % Additional Enumeration Environment Settings
  \usepackage{geometry}            % Page Layout
  \usepackage{soul}                % Text Highlighting
  \usepackage{graphicx}            % Images
  \usepackage{csquotes}            % Quoting Environment
  \usepackage{bookmark}            % Required by `csquotes'
  \usepackage{mdframed}            % Colorful Tex-Box Environment
  \usepackage[toc]{appendix}       % Appendix
  \usepackage{fancyhdr}            % Headings and Footers
  % \usepackage[%
    % style=apa,%
    % sortcites=true,%
    % sorting=nyt%
  % ]{biblatex}
  \usepackage{xcolor}

  % Bibliography Setup
  %% Language Mappings
  % \DeclareLanguageMapping{english}{english-apa}
  % \DeclareLanguageMapping{american}{american-apa}
  %% Bibliography File Path
  % \addbibresource{main.bib}

  % Hyperlink Setup
  \hypersetup{
    colorlinks = true,
    urlcolor = blue,
    linkcolor = blue,
    citecolor = blue
  }

  % Page and Text Layout
  \geometry{%
    a4paper,%
    top=1in,%
    bottom=1in,%
    left=1in,%
    right=1in%
  }
  \setlength{\headheight}{15pt}

  % Header
  \lhead{COM125CG1-M3D2}

  % Title Page
  \title{%
    M3D2: Improving YOUR Interpersonal Communication Skills
  }
  \shorttitle{Module 3 Discussion 2}
  \author{Ashton Hellwig}
  \authorsaffiliations{Department of Mathematics, Front Range Community College}
  \course{COM125: Interpersonal Communication}
  \professor{Richard Thomas}
  \duedate{November 21, 2020 23:59:59 MDT}
  \date{\today}
  \abstract{%
    \textbf{Overview}\\%
    In Module 1 you committed to becoming a better interpersonal communicator by
      focusing on improving two interpersonal communication skills. In each
      subsequent module, we are checking in to see how those efforts are
      proceeding based on your practice sessions. In this module, you will
      report on how your practice has progressed so far.\\%

    You should spend approximately 4 hours on this assignment.%
  }

\begin{document}
  % Title Page
  \maketitle

  % Initial Post
  \section{Initial Post}
    \subsection*{Instructions}
      \begin{enumerate}
        \item To assist the readers of your Main post, list again the two
          interpersonal communication skills you chose to improve.
        \item Friendly reminder: Attach to the Main post a Microsoft Word
          document a Progress Report containing detailed practice sessions
          demonstrating attempts to improve the two communication skills you
          have chosen to improve.
        \item In your main post, include the following:
          \begin{itemize}
            \item Provide specific examples of things you did in your personal
              life and professional life to improve those skills since the last
              module. You should have at least one example per skill. You may
              pull examples from practice sessions contained in your Word
              document.
            \item Tell us about something you practiced from the past module
              that was a success story or maybe did not go so well. This is
              your opportunity to ask specific questions or seek advice from
              your classmates and instructor.
            \item Consider the topics of listening and self-disclosure. Then
              respond to the following in the same post:
              \begin{itemize}
                \item You have already considered how Erin Brokovich listened to
                  Ed in the movie clip. If you were in that same scenario, would
                  you have approached Erin the same way Ed did? Why or why not?
                  What role does his presentation of the check play in their
                  misunderstanding? Use evidence from your readings to support
                  your post.
                \item Erin becomes very upset with Ed during the scene. This
                  leads her to say some things that may not be appropriate in
                  the workplace. Share an event in your past when you said
                  something at work that was inappropriate, or perhaps disclosed
                  information about yourself that you didn’t mean to. What was
                  the result? Is self-disclosure a problem you have? Would you
                  do the same or behave differently next time based on what you
                  have read?
              \end{itemize}
          \end{itemize}
        \item Choose one of the two options below to add to your list of
          interpersonal communication skill improvement:
          \begin{enumerate}
            \item Option One:
              \begin{itemize}
                \item \textbf{If you do not already have listening as one of
                  your skills to improve}, choose one effective listening skill
                  from your list and add it to your plans.
                \item \textbf{If you do already have listening as one of your
                  skills to improve}, which of the effective listening skills
                  on your list will be most helpful to your efforts?
              \end{itemize}
            \item Option Two:
              \begin{itemize}
                \item Do you feel that you may self-disclose too much
                  information in your personal life or professional life? What
                  makes you feel that way? Commit to one step you will take to
                  change that.
              \end{itemize}
          \end{enumerate}
      \end{enumerate}


    \newpage
    \paragraph{Placeholder}
      Placeholder.

  % Replies
  % \include{tex/01-response.tex}
  % \include{tex/02-response.tex}

  % Bibliography
  %% Works Cited
  % \newpage
  % \printbibliography[%
    % title={Works Cited},%
    % heading={bibintoc},%
    % notcategory={consulted}%
  % ]

  %% Works Consulted
  % \newpage
  % \nocite{*}
  % \printbibliography[%
    % title={Works Consulted},%
    % heading={bibintoc},%
    % category={consulted}%
  % ]
\end{document}
